---
title: "Real vs Fake News"
author: "LeTicia Cancel"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Introduction


# Literature Review



# Hypothesis or Reasearch Question


# Data and Variables

```{r}
# libraries
library(quanteda)
library(dplyr)
library(tidytext)
library(tm)
library(topicmodels)
library(data.table)
library(ggplot2)
library(gridExtra)
```


```{r}
# import the data
fake_df <- read.csv("https://github.com/ltcancel/DATA698/blob/main/Data/Fake.csv?raw=true")
real_df <- read.csv("https://github.com/ltcancel/DATA698/blob/main/Data/True.csv?raw=true")
```

```{r}
# preview raw data
#head(fake_df)
#head(real_df)
print("Summary of 'Fake' Dataset")
summary(fake_df)

print("Summary of 'Real' Dataset")
summary(real_df)
#str(real_df)
```

Other summaries
```{r}
fake_df %>%
  count(subject, sort = TRUE)

real_df %>%
  count(subject, sort = TRUE)
```

Missing Values
```{r}
print("'Fake' Dataset Missing Values")
summary(is.na(fake_df))
print("'Real' Dataset Missing Values")
summary(is.na(real_df))
```



```{r}
# clean the data  using tidytext
fake_words <- fake_df %>%
  unnest_tokens(word, text)

# remove stop words
fake_words <- fake_words %>% anti_join(stop_words, by = "word")

# count each word
fake_count <- fake_words %>% 
  count(word, sort = TRUE)
head(fake_count)
```

```{r}
# clean the data  using tidytext
real_words <- real_df %>%
  unnest_tokens(word, text)

# remove stop words
real_words <- real_words %>% anti_join(stop_words, by = "word")

# count each word
real_count <- real_words %>% 
  count(word, sort = TRUE)

#remove weird character
real_count <- real_count %>%
  filter(word != 'â')

head(real_count)
```

chart of words
```{r fig.height=8, fig.width=15}
p1 <- head(fake_count) %>%
  ggplot(aes (word, n, fill = word)) +
  geom_col(stat = "identity") + 
  coord_flip() + 
  labs(title = "Fake News Top Words",
         y = "count") +
  theme(legend.position = "none")


p2 <- head(real_count) %>%
  ggplot(aes (word, n, fill = word)) +
  geom_col(stat = "identity") + 
  coord_flip() + 
  labs(title = "Real News Top Words",
         y = "count") +
  theme(legend.position = "none")

grid.arrange(p1, p2, ncol = 2)
```



Normalizing the data by case-folding, stopword removal, stamming, lemmatization, and contraction simplification
```{r}
# clean the data using Text Mine (TM)
# create a corpus from the fake_df file
fake_df.corpus <- Corpus(VectorSource(fake_df))

space <- content_transformer(function(x, pattern) gsub(pattern, " ", x))
fake.corpus <- tm_map(fake_df.corpus, space, "/")
fake.corpus <- tm_map(fake.corpus, space, "@")
fake.corpus <- tm_map(fake.corpus, space, "\\|")
#remove stopwords
#fake.corpus <- tm_map(fake_df.corpus, removeWords, stopwords("english"))
# convert to lower
fake.corpus <- tm_map(fake_df.corpus, content_transformer(tolower))
#remove numbers
fake.corpus <- tm_map(fake_df.corpus, removeNumbers)
#remove punctuations
fake.corpus <- tm_map(fake_df.corpus, removePunctuation)
#strip white spaces
fake.corpus <- tm_map(fake_df.corpus, stripWhitespace)
# stemming
fake.corpus <- tm_map(fake.corpus, content_transformer(stemDocument))

#head(fake.corpus)
```

Create Document Term Matrix (DTM)
```{r}
# first DTM
fake.dtm <- DocumentTermMatrix(fake.corpus)
fake.dtm <- as.matrix(fake.dtm)
# remove low frequency words (sparse terms)
#fake.dtm2 <- removeSparseTerms(fake.dtm, sparse = 0.99)
#inspect(fake.dtm2)
#??inspect
#convert to dataframe
fake.dtm.sort <- sort(rowSums(fake.dtm), decreasing = TRUE)
fake.dtm.sort <- as.data.frame(word = names(fake.dtm.sort), freq = fake.dtm.sort)
fake.dtm
#write.csv(fake.dtm.df,"DTM.csv")
```

```{r}
# sort by decreasing order
x <- mapply(sum, fake.dtm.df)
colSums(fake.dtm.df)
fake.dtm.sort <- data.frame(fake.dtm.sort)
fake.dtm.sort <- order(fake.dtm.sort, decreasing = TRUE)

fake.dtm.sort
#transpose df
summary(fake.dtm.sort)
fake.dtm.d <- data.frame(word = names(fake.dtm.sort), freq=fake.dtm.sort)
head(fake.dtm.d)
```


Topic modeling. Using latent Dirichlet allocation (LDA) to learn the essential words in our DTM
```{r}
dtm_s <- sort(rowSums())

# LDA 
fake.lda <- LDA(fake.dtm2, k = 2, control = list(seed = 1234))


?LDA
```


# Statistical Methods



# Reference



# Appendix


# Results


# Conclusion



# Abstract






